### 2020-03-18 Thesis-Chapter1-Introduction.tex
Refactor background and intro

\begin{itemize}
    \item In the pursuit of data privacy, legislative action is part of the threat model--and action is likely
    \item If the technical community acts, we can not only be prepared for regulation, but lead and shape it
\end{itemize}

@@

\begin{itemize}
    \item The failure to convince legislative bodies and law enforcement agencies demands that the technical community continue the discussion
    \item The ability to access digital data is important and will be increasingly important for investigations
    \item Various forms of encryption are foundational all elements of online security
    \item Mass surveillance is a grave danger that representative governments are not immune from
    \item International and human rights considerations significantly constrain workable solutions
    \item Transparency to data access is critical for public trust
\end{itemize}

@@

\begin{itemize}
    \item Argument maps formalizing the debate
    \item A broad threat model describing the environment
    \item A structure for organizing future progress
\end{itemize}

>>>>

\begin{itemize}
    \item In the pursuit of data privacy, regulatory action is part of the threat model--and action is likely
    \item If the technical community acts, we can not only be prepared for regulation, but lead and shape it
\end{itemize}

@@

\begin{itemize}
    \item The failure to convince legislative bodies and law enforcement agencies demands that the technical community continue the discussion
    \item The ability to access digital data is important and will be increasingly important for investigations
    \item Various forms of encryption are foundational all elements of online security
    \item Mass surveillance is a grave danger that representative governments are not immune from
    \item International and human rights considerations significantly constrain workable solutions
    \item Transparency to data access is critical for public trust
    % \item In pluralistic societies, government is obligated to respect and balance opposing viewpoints
\end{itemize}

@@

The paper serves to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief history of encryption regulation, technology, and conflict, it introduces argument maps and threat models using
data flow diagrams. In the following chapters it analyzes exceptional access arguments in detail and creates a
multi-level threat model, broken down by the significantly different challenges posed by data at rest and data in
motion. The paper concludes with a set of policies and principles to apply to the problem in light of valid arguments
and threats.

% \begin{itemize}
%     \item Argument maps formalizing the debate
%     \item A broad threat model describing the environment
%     \item A structure for organizing future progress
% \end{itemize}

### 2020-03-18 Thesis-Chapter2-Background.tex
Refactor background and intro

@@

\section{Exceptional Access: Arguments For and Against}
\label{sec-argsbackground}

The debate over exceptional access takes place on two fundamental levels:
\begin{enumerate}
    \item Whether cryptosystems with exceptional access represent a net benefit to society
    \item Whether and how to conduct exceptional access research
\end{enumerate}

These arguments are introduced here and analyzed in detail in \mychap{chap-arguments}.
[This section is currently written in outline-format, but will be drafted in a narrative, introductory style, as these
arguments are the focus of a later chapter.]

\subsection{Arguments For}

Why EA is a benefit to society:
\begin{itemize}
    \item Absolute privacy is not a right
    \item Encryption gives too much power to the individual
    \item EA would allow more crimes to be prevented and prosecuted
\end{itemize}

Why to research EA:
\begin{itemize}
    \item EA done well would be more secure and privacy preserving than EA done poorly
    \item The threat of legislative action creates urgency
\end{itemize}

\subsection{Arguments Against}

Why EA is a danger to society:
\begin{itemize}
    \item Privacy is an absolute right
    \item Exceptional access gives too much power to the state
    \item Exceptional access is not possible in an acceptably secure manner
\end{itemize}

Why not to research EA:
\begin{itemize}
    \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
            them
    \item The technical community should not entertain delusions about what is truly possible
\end{itemize}

\section{Regulatory Environment}

\subsection{US Efforts to Regulate Encryption}

\subsection{Regulations around the World}

\section{Technical Approaches}

\subsection{Historical Approaches}

@@

\subsection{Modern Proposals}

@@

>>>>

This chapter summarizes the history of encryption and the exceptional access debate, introduces argument maps, and
introduces threat modeling with data flow diagrams.

\section{A Brief History of Encryption}
\label{sec-history}

@@

\subsection{Regulatory Environment}
\label{sec-reg-environment}

\subsubsection*{US Efforts to Regulate Encryption}

\subsubsection*{Regulations around the World}

\subsection{Technical Approaches}
\label{sec-tech-approaches}

\subsubsection*{Historical Approaches}

@@

\subsubsection*{Modern Proposals}

@@

\section{Argument Maps}
\label{sec-arg-maps-intro}

\section{Threat Models and Data Flow Diagrams}
\label{sec-threat-model-intro}

### 2020-03-18 Thesis-Chapter3-Arguments.tex
Add some new sources
Refactor background and intro

In this chapter, develop the arguments introduced in \mysec{sec-argsbackground}. Make use of argument maps to break down
and visualize the debate, as shown in \myfig{fig-args-top-level}.

% \includepdf[]{arguments/build/top-level.pdf}
\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{arguments/build/top-level.pdf}
    \caption[Argument: Top Level]{Top level arguments for and against exceptional access.}
    \label{fig-args-top-level}
\end{figure}

>>>>

In this chapter, develop the arguments employed in EA debates. Make use of argument maps to break down and visualize the
debate, as shown in \myfig{fig-args-top-level}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{arguments/build/top-level.pdf}
    \caption[Argument: Top Level]{Top level arguments for and against exceptional access.}
    \label{fig-args-top-level}
\end{figure}

The debate over exceptional access takes place on two fundamental levels:
\begin{enumerate}
    \item Whether cryptosystems with exceptional access represent a net benefit to society
    \item Whether and how to conduct exceptional access research
\end{enumerate}

\subsection{Arguments For}

Why EA is a benefit to society:
\begin{itemize}
    \item Absolute privacy is not a right
    \item Encryption gives too much power to the individual
    \item EA would allow more crimes to be prevented and prosecuted
\end{itemize}

Why to research EA:
\begin{itemize}
    \item EA done well would be more secure and privacy preserving than EA done poorly
    \item The threat of legislative action creates urgency
\end{itemize}

\subsection{Arguments Against}

Why EA is a danger to society:
\begin{itemize}
    \item Privacy is an absolute right
    \item Exceptional access gives too much power to the state
    \item Exceptional access is not possible in an acceptably secure manner
\end{itemize}

Why not to research EA:
\begin{itemize}
    \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
            them
    \item The technical community should not entertain delusions about what is truly possible
\end{itemize}
